Deterministic and statistical truncated KdV models for anomalous waves induced by abrupt depth change

### 2018-09-23 LatexNotes/Notes.tex
Sorting out KdV scales.

We will be using the truncated KdV equations (TKDV) with variable depth, in particular an abrupt depth change (ADC). The upstream depth is normalized to $1$ and the downstream (dimensionless) depth is $D_0$. Accordingly, the upstream and downstream Hamiltonians are given by
\begin{align}
\label{Hamiltonian}
& H^- = E_0^{1/2} H_3 - H_2 \\
& H^+ = D_0^{-13/4} E_0^{1/2} H_3 - D_0^{3/2} H_2 \\
\end{align}

>>>>

\subsection{The KdV equation}

Following Johnson's derivation the dimensionless KdV equation is (on page 208)
\begin{equation}
2 \eta_{\tau} + 3 \eta \eta_{\xi} + \frac{1}{3} \eta_{\xi \xi \xi} = 0
\end{equation}
I had to work backwards quite a bit to figure out how this was non-dimensionalized (Johnson keeps rescaling things over and over again). Ultimately, the characteristic scales are
\begin{align}
& Z^* = h_0 , \quad X^* = \eps^{-1/2} h_0 , \quad T^* = \eps^{-1/2} \sqrt{h_0/g} , \\
& W^* = \eps^{3/2} \sqrt{g h_0} , \quad U^* = \eps \sqrt{g h_0} , \quad P^* = \eps \rho g h_0
\end{align}
where $\eps$ is the ratio of characteristic amplitude to depth
\begin{equation}
\eps = a / h_0
\end{equation}
The variables $\tau$ and $\xi$ are
\begin{align}
\tau = \eps t , \quad \xi = x-t
\end{align}
Remember, the privileged KdV scaling is $\delta^2 \sim \eps$ where $\delta = h_0 / \lambda$. If this scaling is inserted into above, then $X^* \sim \lambda$, $T^* \sim \lambda/\sqrt{g h_0}$ which all makes sense.

\subsection{Hamiltonian structure}
We will be using the truncated KdV equations (TKDV) with variable depth, in particular an abrupt depth change (ADC). The upstream depth is normalized to $1$ and the downstream (dimensionless) depth is $D_0$. Accordingly, the upstream and downstream Hamiltonians are given by
\begin{align}
\label{Hamiltonian}
& H^- = E_0^{1/2} H_3 - H_2 \\
& H^+ = D_0^{-13/4} E_0^{1/2} H_3 - D_0^{3/2} H_2 \\
\end{align}
